The cost of undisturbed landscapes

### 2020-04-30 projects/asparagus/doc/slides.tex

    \begin{frame}
        \frametitle{The cost of undisturbed landscapes}
        \framesubtitle{Estimating the opportunity cost of wind power}
        To determine the opportunity cost of substituting wind power with solar PV, we
        \begin{enumerate}
            \item derive the unrestricted system cost-minimizing deployment of wind and solar power \label{step1}
            \item restrict deployment of wind power by a small margin (so that the next best RET substitutes for wind power) and
            observe net system cost $c_{net}$ (calculated as total system cost including air pollution cost net of trade balance) \label{step2}
            \item repeat \ref{step2} till no wind power can be deployed
            \item the opportunity cost of wind power is approximated by the change in $c_{net}$ in response to a change in wind
            power capacity $w$ deployed.
            \begin{align*}
                OC_w = \frac{\Delta c_{net}}{\Delta w}
            \end{align*}
        \end{enumerate}
    \end{frame}

@@

    \section{Results}
    \begin{frame}
        \frametitle{The cost of undisturbed landscapes}

        \begin{textblock*}{10cm}
            (1.25cm, 1.75cm) % {block width} (coords)
            \centering
            \begin{tikzpicture}
                \draw (4.5,0.0) node[] {\small Opportunity Cost of Wind Power};
            \end{tikzpicture}
        \end{textblock*}

@@

                \vspace{3.75cm}
                \quad wind power and solar PV \\ \quad are substitutes
            \end{small}
        \end{textblock*}
    \end{frame}

    \begin{frame}
        \frametitle{The cost of undisturbed landscapes}

        \begin{textblock*}{10cm}
            (1.25cm, 1.75cm) % {block width} (coords)
            \centering
            \begin{tikzpicture}
                \draw (4.5,0.0) node[] {\small Opportunity Cost of Wind Power};
        \end{tikzpicture}
    \end{textblock*}

@@

    \begin{frame}
\frametitle{The cost of undisturbed landscapes}
\framesubtitle{Cost with restricted wind power}
\begin{textblock*}{10cm}(0.75cm, 2.0cm) % {block width} (coords)
\includegraphics[width=\textwidth, keepaspectratio]{./figures/cost}
\end{textblock*}

@@

 %%%Last Frame
 {
    \usebackgroundtemplate{
        \begin{picture}(320,290)
        \hspace{9.5cm}
          \includegraphics[width=0.6\linewidth]{./logos/refuel_logo_with_text}
%        \begin{picture}(200,305)
%        \hspace{7.7cm}
%          \includegraphics[width=0.6\linewidth]{refuel_logo_with_text}
        \end{picture}
    }
    \begin{frame}
        \frametitle{Thank you!}
        \vspace{0.5cm}
        \url{https://refuel.world}\\
        \url{https://github.com/inwe-boku/medea}\\
        \url{sebastian.wehrle@boku.ac.at}

>>>>

    \begin{frame}
        \frametitle{The cost of undisturbed landscapes}
        \framesubtitle{Estimating the opportunity cost of wind power}
        To determine the opportunity cost of wind power versus solar PV, we
        \begin{enumerate}
            \item derive the unrestricted system cost-minimizing deployment of wind and solar power \label{step1}
            \item restrict deployment of wind power by a small margin (so that the next best RET substitutes for wind power) and
            observe net system cost $c_{net}$ in the country of interest (calculated as total system cost including air
            pollution cost net of trade balance) \label{step2}
            \item repeat \ref{step2} till no wind power can be deployed anymore
            \item the opportunity cost of wind power is approximated by the change in $c_{net}$ in response to a change in wind
            power capacity $w$ deployed.
            \begin{align*}
                OC_w = \frac{\Delta c_{net}}{\Delta w}
            \end{align*}
        \end{enumerate}
    \end{frame}

@@

    \section{Results}
    \begin{frame}
        \frametitle{The cost of undisturbed landscapes}
        \framesubtitle{Relative measure of substitution}
        \begin{textblock*}{10cm}
            (1.25cm, 1.75cm) % {block width} (coords)
            \centering
            \begin{tikzpicture}
                \draw (4.5,0.0) node[] {\small Opportunity Cost of Wind Power};
            \end{tikzpicture}
        \end{textblock*}

@@

                \medskip
                At $\Phi=1$ RET deployment is as in the unconstrained system cost minimum.

                \smallskip
                At $\Phi=0$ the least cost technology is fully substituted by its best alternative.
            \end{small}
        \end{textblock*}
    \end{frame}

    \begin{frame}
        \frametitle{The cost of undisturbed landscapes}
        \framesubtitle{Absolute measure of substitution}
        \begin{textblock*}{10cm}
            (1.25cm, 1.75cm) % {block width} (coords)
            \centering
            \begin{tikzpicture}
                \draw (4.5,0.0) node[] {\small Opportunity Cost of Wind Power};
            \end{tikzpicture}
        \end{textblock*}

@@

    \begin{frame}
        \frametitle{The cost of undisturbed landscapes}
        \framesubtitle{Cost with restricted wind power}
        \begin{textblock*}{10cm}
            (0.75cm, 2.0cm) % {block width} (coords)
            \includegraphics[width=\textwidth, keepaspectratio]{./figures/cost}
        \end{textblock*}

        \begin{textblock*}{4cm}
            (11cm, 2.25cm)
            \begin{small}
                \begin{table}
                    \begin{tabular}{p{1.8cm} | p{0.3cm} l}
                        Capital cost of solar PV & $630$ & \SI{}{\text{\euro}\per\kilo\watt\text{p}} \\
                        \ce{CO2} price & $90$ & \SI{}{\text{\euro}\per\mega\watt\hour}
                    \end{tabular}
                \end{table}
            \end{small}
\end{textblock*}

@@

    %%%Last Frame
    {
        \usebackgroundtemplate{
            \begin{picture}
                (320,290)
                \hspace{9.5cm}
                \includegraphics[width=0.6\linewidth]{./logos/refuel_logo_with_text}
%        \begin{picture}(200,305)
%        \hspace{7.7cm}
%          \includegraphics[width=0.6\linewidth]{refuel_logo_with_text}
        \end{picture}
    }
    \begin{frame}
        \frametitle{Thank you!}
        \vspace{0.5cm}
        \url{https://refuel.world}\\
        \url{https://github.com/inwe-boku/medea}\\
        \url{sebastian.wehrle@boku.ac.at}
